\chapter[Concerning the Ring]{One does not simply walk into Mordor}

The talk did not die down in nine or even ninety-nine days. Indeed, the
story of \textcolor{RawSienna}{\textsc{\LARGE Banger Baggins}}, who used to run around naked at night and ravish
young maidens, became a favourite story, not least among those who could lay
a claim to belonging to that category. Frodo, however, remained wed to
celibacy. He lived alone, as Bilbo had done; but he had a good many friends,
especially among the younger hobbits. His closest friends were Pipsqueak
Took and Moribund ("Morrie" or "the Mobster") Brandybuck, one of them
friendly and willing if somewhat pimply, the other as cold as ice and as
ruthless as a society hostess. Not for nothing were Morrie and his family
feared throughout the Shire, even by the Shirriffs though those were all on
the Brandybuck paylist.
  Frodo enjoyed being his own master and the Mr Baggins of Bag End. He
lived on quietly, increasing his inherited fortune through wise investments
and high-interest loans which earned him the nickname of "Sharkey", until
his fiftieth birthday drew near. Then Gandalf turned up again. Frodo
welcomed his old friend with surprise and great delight. They looked hard at
one another.
  "You are becoming grossly fat, Frodo," said Gandalf. "Luckily, I have some
really good exercise in store for you."
  "You are too kind," murmured Frodo. "Please don't exert yourself on my
behalf."
  "I'm afraid I have to," replied the wizard. "That ring of yours - do you
still have it?"
  "Yes, of course," said Frodo. "I would gladly get rid of it; every time
I've tried it on I kept stumbling over my own invisible feet since I could
not see them. I wish I had never accepted the pesky thing. Will you not take
the ring, Gandalf!"
  "No!" cried Gandalf, springing to his feet. "That ring would bugger up my
spells completely. No, no, I refuse! But I can give you some advice about
how to get rid of it, if you want."
  "What is that?" demanded Frodo.
  "Take it to Mordor and drop it in the Cracks of Doom," said Gandalf. "If
you don't, Sauron will come and take it. And you don't want him to do that;
he gets pissed off at people who have touched his precious ring." He lit a
cigar. "But if you put an end to the ring, you off Sauron too. The little
dimwit infused so much of himself in the ring that his destruction with it
is certain."
  "But I remember how you once told me that Sauron thought the ring had been
destroyed."
  "I did. He thought it had been thrown into the \textcolor{RedOrange}{\textsc{\LARGE Cracks of Doom}}, as should
have happened. Now, however, he knows that it isn't so."
  "But how can he have thought any such thing? If the ring had been
destroyed he wouldn't have been around; so he should have realized that the
ring had not been destroyed."
  "As I told you, he is a dimwit. He really is incredibly stupid.All the
same, there was a scholarly article in The Minas Tirith Review about the
Ring yesterday, written by the learned Dr Faramir. Sauron must have read
that article; he subscribes to an excellent newscutting agency. His
emissaries may be on their way to the Shire at this very moment."
  "I had better leave at once," said Frodo.
  "I agree," said Gandalf. Suddenly he stopped as if listening. Frodo became
aware that all was very quiet, inside and outside. Gandalf crept to one
side of the window. Then with a dart he sprang to the sill, and thrust a
long arm out as if to catch somebody. Then his movement stopped. He
straightened up and snorted.
  "No one has been eavesdropping," he said. "Excellent. You'd better leave
as soon as possible, Frodo. Take that servant of yours, Sam, with you. He
looks like a sturdy lad and might come in useful."
